\documentclass[a4paper,11pt]{report}
\usepackage[a4paper,textwidth=37em,vmargin=30mm]{geometry}
\usepackage{calc,xeCJK,xeCJKfntef,paralist,enumitem,tabu,booktabs,xunicode,amssymb,amsmath}
\usepackage{eso-pic,graphicx,datetime2,multicol,indentfirst,tocloft}
\usepackage[hidelinks]{hyperref}

\setmainfont[Numbers=Lining]{Brygada 1918}
\setromanfont[Numbers=Lining]{Brygada 1918}
\setsansfont[Numbers=Lining]{Nimbus Sans}
\setmonofont{Elite Math}
\setCJKmainfont{Noto Serif CJK SC}
\setCJKromanfont{Noto Serif CJK SC}
\setCJKsansfont{Noto Sans CJK SC}
\setCJKmonofont{Noto Sans CJK SC}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\frenchspacing
\linespread{1.2}

\title{Immerherbstreich Settings Book}
\author{Neruthes}
\date{\today}




\begin{document}
\begin{titlepage}
	\maketitle
\end{titlepage}
\tableofcontents
\clearpage

\chapter{Geography}
\section{Geography Overview}

Immerherbstreich is a rather small island-based country.

The Reich consists of 1 special city and 4 provinces.

The special city is Kramuchdort\footnote{Kramuchdort: 克拉幕多.}, the capital city of the Reich.

The 4 provinces are
Havarina\footnote{Havarina: 哈瓦瑞那.},
Olingkurt\footnote{Olingkurt: 欧凌库特.},
Rheiton\footnote{Rheiton: 莱顿.},
and Bodomuch\footnote{Bodomuch:博多幕.}.

\section{Kramuchdort}

The special city Kramuchdort consists of Kramuchdort Municipality and 4 suburban regions:
Regendorf, Regenbogendorf, Rindfjord, and Harzheim.

\subsection{Kramuchdort Municipality}

Kramuchdort Municipality consists of 4 districts:
Rabenschwarzbezirk, Sommerbezirk, Schneesturmbezirk, Balladebezirk.

\subsubsection{Rabenschwarzbezirk}

Rabenschwarzbezirk is where Herbstnachtschloss is located.

Rabenschwarzbezirk includes 12 streets:
Nachtrabe Allee,
and others yet to be named.

{\sffamily\bfseries Nachtrabe Allee}

\begin{compactenum}
    \item Herbstnachtschloss, Kaiserliches Gericht (Imperial Court)
    \item Herbstnachtschloss, Private communications for the imperial family
    \item Herbstnachtschloss, Palace management office
    \item Herbstnachtschloss, Staff communications for work usage
    \item Herbstnachtschloss, Staff communications for personal usage
    \item Herbstnachtschloss, Reserved code for future allocation
    \item Herbstnachtschloss, Reserved code for future allocation
    \item Reichskanzler Official Residence, Official usage
    \item Reichskanzler Official Residence, Private usage
    \item Cabinet Headquarter `Dämmerung Halle' (Twilight Hall)
    \item Parliament, Reichsrat (House of Lords)
    \item Parliament, Reichstag (House of Commons)
    \item Home Office
    \item Foreign Office
    \item Treasury Office
    \item Department of Defense
    \item Department of Justice
    \item Department of Commerce
    \item Department of Energy
    \item Department of Environment
    \item Department of Technology
    \item Administration of Border Protection
    \item Administration of Taxation
    \item Administration of Food and Drug
    \item Imperial Post Service
    \item Internal Revenue Service
    \item Bureau of Publication
    \item Common Quango House Alpha
    % \item Imperial Academy of Science
    % \item Supreme Court
\end{compactenum}

\subsubsection{Sommerbezirk}
// TODO

\subsubsection{Schneesturmbezirk}
// TODO

\subsubsection{Balladebezirk}
// TODO



\section{Havarina}
// TODO

\section{Olingkurt}
// TODO

\section{Rheiton}
// TODO

\section{Bodomuch}
// TODO


\end{document}
